Self-test prime dimensional EPR pairs with constant alphabet

### 2019-01-09 Draft/draft.tex
a more formal self-test proof

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}[1]{\sigma_x^{(#1)}}
\newcommand{\pauliz}[1]{\sigma_z^{(#1)}}
\newcommand{\G}[1]{G^{(#1)}}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}

@@

\textbf{The Pauli operators.} 
We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators behave like 
the $d$-dimensional Pauli operators which are defined by
\begin{align}
	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1}{i} \quad \pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i\ketbra{i}{i}
\end{align}
where $\omega_d = e^{i\pi/d}$ is the primitive $d$th root of unity and the addition is taken modulo $d$.

@@

The main tool to understand linear system game is through its solution group over $\Z_d$.
\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
	\begin{align}
		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
	\end{align}
	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
	\begin{align}
		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
	\end{align}
	Then the solution group has presentation 
	\begin{align}
	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
	\end{align}
\end{definition}
Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
\begin{definition}[Operator solution]
	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
	representation mapping $\J$ to $\overline{\omega_d}\1$.
\end{definition}
What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
linear system game from its operator solution and vice versa.
%========================================
\section{Components of $\G{d}$}
%========================================
Suppose we would like to self-test $\ket{\EPR{d}}$ with $\G{d}$, where $d$ is prime and has primitive root $2$.
Later we will see how to deal with general prime numbers and why there are infinitely many prime dimensional EPR pairs 
that can be self-tested by a variant of $\G{d}$.
%----------------------------------------------------------------
\subsection{The linear system game}
%----------------------------------------------------------------
The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the 
following group
\begin{align}
	\Pg_{\LS} = \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}
%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
%by the following relations
%\label{eq:sim}
%	u_x x u_x = x^2, \quad
%	u_z z u_z = z^2.
%Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
%relation $xzx^{-1}z^{-1} = \J$.
%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
%we can verify that 
%	U_xU_z = \1 = U_zU_x,
%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
%In the end, we define $\Pg_{\LS}$ by
%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.
See Appendix~\ref{sec:construct} for details.
%------------------------------------------------------------------------
\subsection{The extended weighted CHSH game}
%------------------------------------------------------------------------
The extended weighted CHSH game is added to make sure that some of Alice and Bob's observables have
eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
The notation for the extended weighted CHSH game that enforces the eigenvalues of the observable $U$ is 
$\CHSH_U$, where the superscript $d$ means that the rules of this game depends on $d$.
Intuitively, this is one step towards verifying Alice and Bob use $\paulix{d}$ and $\pauliz{d}$ in their operator solution.

@@

We summarize the projectors of the ideal strategy and the ideal correlation in the following two charts.
Note that we don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ because they are irrelevant
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{2}{|c|}{$x=\ast$}\\
\cline{3-4}
\multicolumn{2}{|c|}{} &$a = \diamond$ & $a = \perp$ \\
\hline
\hline
\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & 2/d & 0 \\
\cline{2-4}
&$b=\perp$ & 0 & (d-2)/d \\
\hline
\end{tabular}
\caption{Alice and Bob's behaviour when $x=y=\ast$.}
\end{center}
\end{table}

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{3}{|c|}{$x=0$}&
\multicolumn{3}{|c|}{$x=1$} \\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$a = 0$ & $a=1$ & $a=\perp$ &
$a = 0$ & $a=1$ & $a=\perp$\\
\hline
\hline
\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $1/d$ & $1/d$ & 0 
& $1/d$ & $1/d$ & 0 \\
\cline{2-8}
&$b=\perp$ & 0 & 0 & $\frac{d-2}{d}$ 
&  0 & 0 & \small $\frac{d-2}{d} $  \\
\hline
\end{tabular}
\end{center}
\caption{Alice and Bob's behaviour when $x\in [2]$ and $y = \ast$.}
\end{table}
Alice's projectors are 
\begin{align*}
	&A_\ast^\diamond = \Pi_V, A_\ast^\perp = \Pi_V^\perp \\
	&A_0^0 = \ketbra{u_1}{u_1}, A_0^1 = \ketbra{u_{d-1}}{u_{d-1}}, A_0^\perp = \Pi_V^\perp\\
	&A_1^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
	A_0^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_0^\perp = \Pi_V^\perp
\end{align*}
Bob's projectors are 
\begin{align*}
	&B_\ast^\diamond = \Pi_V, B_\ast^\perp = \Pi_V^\perp \\
	&B_0^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} + \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{4d})\bra{u_1} + \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} - \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{4d})\bra{u_1} - \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
	&B_1^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} - \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{4d})\bra{u_1} - \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} + \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{4d})\bra{u_1} + \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right).
\end{align*}
About Bob's projectors for input $y \in [2]$, we are only interested in their actions when restricted 
to the subspace $V$. Their actions on the subspace $V^\perp$ is irrelevant in this game.

The importance of this game is summarized in the following lemma.
\begin{lemma}
	\label{lm:chsh_comp}
	Suppose a quantum strategy $\left(\{\{\tA_x^a\}_a\}_x, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}\right)$
	achieves the optimal correlation of $\CHSH$, then there exists unitaries $U_A$ and $U_B$ 
	such that 
	\begin{align*}
		&U_A\x U_B \left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) = \ket{\EPR{2}} \\
		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 + \tB_1}{2\cos(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
		=\1 \x \pauliz{2} \ket{\EPR{2}} \\
		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 - \tB_1}{-2\sin(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
		=\1 \x \paulix{2} \ket{\EPR{2}} 
	\end{align*}
	where $\tB_0 = \tB_0^0 - \tB_0^1$ and $\tB_1 = \tB_1^0 - \tB_1^1$.
\end{lemma}
\begin{proof}
Note that $\tA_x^a \tB_y^b$ means $\tA_x^a \x \tB_y^b$ in the following proof.

@@

%-----------------------------------------------------------------
\subsection{Proof}
%-----------------------------------------------------------------
\hl{This subsection needs to be formalized.}
By Lemma~$4.3$ of \cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
of the linear system game: 
For each variable $\{ x_i \}_{i=1}^n$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
The condition that they agree with assignment to variables means that 
\begin{align}
	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
\end{align}
and the condition that Alice's assignments satisfy the constraint means that 
\begin{align}
	\Tr(\rho_A \Pi_{j: A_{ij} \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m
\end{align}
where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$, so for  any $\ket{v} \in \supp(\rho_A)$,
we have 
\begin{align}
\Pi_{j:A_{ij} \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m.
\end{align}
Since the relation $u^{-1}xu = x^2$ is embedded in this linear system game, we know
\begin{align}
	\sigma_A(u)^\dagger A_1A_2 \sigma_A(u) \ket{v}= (A_1A_2)^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
\end{align}
For simplicity, we define $X = A_1A_2$ and $U = \sigma_A(u)$.
For simplicity, we define $X = A_1A_2$ and $U = \sigma_A(u)$.
The condition becomes
\begin{align}
	UXU^\dagger \ket{v} = X^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
\end{align}
On the subspace $\supp(\rho_A)$, we have the equality
\begin{align}
	\label{eq:sim}
	UXU^\dagger X^{-2} = \1.
\end{align}
We will come back to the implication of this condition later.

>>>>

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}[1]{\sigma_x^{(#1)}}
\newcommand{\pauliz}[1]{\sigma_z^{(#1)}}
\newcommand{\G}[1]{G^{(#1)}}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}

@@

\textbf{The Pauli operators.} 
We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators behave like 
the $d$-dimensional Pauli operators which are defined by
\begin{align}
	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1}{i} \quad \pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i\ketbra{i}{i}
\end{align}
where $\omega_d = e^{i\pi/d}$ is the primitive $d$th root of unity.
Through out this paper, any operation on the label of the eigenvector $i$ is taken modulo $d$,
for example, the addition above.

@@

%The main tool to understand linear system game is through its solution group over $\Z_d$.
%\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
%	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
%	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
%	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
%	\begin{align}
%		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
%	\end{align}
%	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
%	\begin{align}
%		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
%	\end{align}
%	Then the solution group has presentation 
%	\begin{align}
%	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
%	\end{align}
%\end{definition}
%Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
%Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
%\begin{definition}[Operator solution]
%	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
%	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
%	representation mapping $\J$ to $\overline{\omega_d}\1$.
%\end{definition}
%What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
%linear system game from its operator solution and vice versa.
%========================================
\section{Components of $\G{d}$}
%========================================
Suppose we would like to self-test $\ket{\EPR{d}}$ with $\G{d}$, where $d$ is prime and has primitive root $2$.
Later we will see how to deal with general prime numbers and why there are infinitely many prime dimensional EPR pairs 
that can be self-tested by a variant of $\G{d}$.
%----------------------------------------------------------------
\subsection{The linear system game}
%----------------------------------------------------------------
The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the 
following group
\begin{align}
	\Pg_{\LS} = \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}
See Appendix~\ref{sec:construct} for details about how to construct $\LS$.

The special property of $\Pg_{\LS}$ is summarized in the following lemma. 
\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		U = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && X = \sum_{i=1}^{d-1}\ketbra{i/2}{i},
	\end{align}
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^2$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices of the set $\{U^k X^l\}_{k \in[d-1]-1, l \in [d-1]}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1]-1, l \in [d-1]}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists integers $\{ k_i \}_{i=1}^{d-1}$ such that $2^{k_i} \equiv i \pmod{d}$.
The fact that $2$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

Starting with $\ket{x_{k_1}}$.
Let's look at the entry $\bra{1}M\ket{1}$ where 
\begin{align}
	\bra{1}M\ket{1} = \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{1}{i/2^k}\braket{i}{1}.
\end{align}
For the term $\braket{1}{i/2^k}\braket{i}{1} \neq 0$ we must have $i = 1$ and $2^k \equiv 1 \pmod{d}$, or equivalently,
$k = k_1$. Hence, we can conclude that 
\begin{align}
	\bra{1}M\ket{1} = \sum_{l = 1}^{d-1} x_{k_1,l}\omega_d^l = 0. 
\end{align}
Similarly we can determine that for all $j = 1,2\dots d-1$,
\begin{align}
	\bra{j}M\ket{j} 
	=  \sum_{k=0}^{d-2}\sum_{l = 1}^{d-1}\sum_{i=1}^{d-1} x_{k, l}\omega_d^{il}\braket{j}{i/2^k}\braket{i}{j} 
	= \sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl} = 0.
\end{align}
Hence we get $d-1$ equations with $d-1$ variables, and the linear system
can be represented by 
\begin{align}
	W \ket{x_{k_1}} = 0,
\end{align}
where $W_{m,n} = \omega_d^{mn}$. Then we define
\begin{align}
	\tW = 
	\begin{pmatrix}
	1 & 1 \\
	1 & W
	\end{pmatrix}.
\end{align}
First observe that $\tW$ is a Vandermonde matrix, hence it is non-singular.
Now we define $\ket{\tx_{k_1}} = (0, x_{k_1,1}, \dots x_{k_1,d-1})^\intercal$ 
and prove that it satisfies the condition
that 
\begin{align}
	\tW \ket{\tx_{k_1}} = 0,
\end{align}
which involves $d$ equations. The last $d-1$ equations are given by the assumption and $M$.
We only need to prove that $\sum_{l=1}^d x_{k_1, l} = 0$, which comes from the first row of $\tW$.
It can be proved by summing the known $d-1$ equations as follows
\begin{align}
	0=\sum_{j = 1}^{d-1} \bra{j}M\ket{j}  
	=  \sum_{j=1}^{d-1}\sum_{l = 1}^{d-1}x_{k_1,l}\omega_d^{jl}
	=\sum_{l = 1}^{d-1}x_{k_1,l} (\sum_{j=1}^{d-1} \omega_d^{jl})
	= \sum_{l = 1}^{d-1}- x_{k_1,l}
\end{align}
where we have used the fact that $\sum_{j=1}^{d-1} \omega_d^{jl} =-1$ for all $l = 1,2\dots d-1$.
Since $\tW$ is non-singluar, we know $\ket{\tx_{k_1}} = 0$ which implies that $\ket{x_{k_1}} = 0$.

For $\ket{x_{k_a}}$, we look at entries $\{\bra{j}M\ket{aj}\}_{j=1}^{d-1}$ for $a = 2 \dots d-1$ and get equations
of the form
\begin{align}
	0 = \bra{j}M\ket{aj} = \sum_{l=1}^{d-1} x_{k_a, l} \omega_d^{ajl} 
\end{align}
The corresponding coefficient matrix has value $\omega_d^{amn}$ at coordinate $m,n$,
so it is also a submatrix of a Vandermonde matrix. Similar argument gives us that $\ket{x_{k_a}} = 0$.

To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices.
\end{proof}
%\begin{align}
%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
%\end{align}
%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
%by the following relations
%\begin{align}
%\label{eq:sim}
%	u_x x u_x = x^2, \quad
%	u_z z u_z = z^2.
%\end{align}
%Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
%relation $xzx^{-1}z^{-1} = \J$.
%
%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
%\begin{align}
%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
%\end{align}
%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
%we can verify that 
%\begin{align}
%	U_xU_z = \1 = U_zU_x,
%\end{align}
%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
%In the end, we define $\Pg_{\LS}$ by
%\begin{equation}
%\begin{aligned}
%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
%\end{aligned}
%\end{equation}
%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.

%------------------------------------------------------------------------
\subsection{The extended weighted CHSH game}
%------------------------------------------------------------------------
The extended weighted CHSH game is added to make sure that some of Alice and Bob's observables have
eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
The notation for the extended weighted CHSH game that enforces the eigenvalues of the observable $U$ is 
$\CHSH_U$, where the superscript $d$ means that the rules of this game depends on $d$.
Intuitively, this is one step towards verifying Alice and Bob use some operator $X$ with eigenvalues
$\{\omega_d^i\}_{i \in [d]}$ in their operator solution of $\LS$.

@@

For completeness, we show the ideal correlation in the following three charts and then give the projectors. 
Note that we don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ because they are irrelevant
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{2}{|c|}{$x=\ast$}\\
\cline{3-4}
\multicolumn{2}{|c|}{} &$a = \diamond$ & $a = \perp$ \\
\hline
\hline
\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & 2/d & 0 \\
\cline{2-4}
&$b=\perp$ & 0 & (d-2)/d \\
\hline
\end{tabular}
\caption{Alice and Bob's behaviour when $x=y=\ast$.}
\end{center}
\end{table}

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{3}{|c|}{$x=0$}&
\multicolumn{3}{|c|}{$x=1$} \\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$a = 0$ & $a=1$ & $a=\perp$ &
$a = 0$ & $a=1$ & $a=\perp$\\
\hline
\hline
\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $1/d$ & $1/d$ & 0 
& $1/d$ & $1/d$ & 0 \\
\cline{2-8}
&$b=\perp$ & 0 & 0 & $\frac{d-2}{d}$ 
&  0 & 0 & \small $\frac{d-2}{d} $  \\
\hline
\end{tabular}
\end{center}
\caption{Alice and Bob's behaviour when $x\in [2]$ and $y = \ast$.}
\end{table}
Alice's projectors are 
\begin{align*}
	&A_\ast^\diamond = \Pi_V, A_\ast^\perp = \Pi_V^\perp \\
	&A_0^0 = \ketbra{u_1}{u_1}, A_0^1 = \ketbra{u_{d-1}}{u_{d-1}}, A_0^\perp = \Pi_V^\perp\\
	&A_1^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
	A_0^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_0^\perp = \Pi_V^\perp.
\end{align*}
Bob's projectors are 
\begin{align*}
	&B_\ast^\diamond = \Pi_V, B_\ast^\perp = \Pi_V^\perp \\
	&B_0^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} + \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{4d})\bra{u_1} + \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} - \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{4d})\bra{u_1} - \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
	&B_1^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} - \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{4d})\bra{u_1} - \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} + \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{4d})\bra{u_1} + \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right).
\end{align*}
About Bob's projectors for input $y \in [2]$, we are only interested in their actions when restricted 
to the subspace $V$. Their actions on the subspace $V^\perp$ is irrelevant in this game.

The robustness of this game is summarized in the following lemma.
\begin{lemma}
	\label{lm:chsh_comp}
	Suppose a quantum strategy $\left(\{\{\tA_x^a\}_a\}_x, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}\right)$
	achieves the optimal correlation of $\CHSH$, then there exists unitaries $U_A$ and $U_B$ 
	and a quantum state $\ket{junk}$
	such that 
	\begin{align*}
		&U_A\x U_B \left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) = \ket{\EPR{2}}\x \ket{junk} \\
		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 + \tB_1}{2\cos(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
		=(\1 \x \pauliz{2} \ket{\EPR{2}}) \x \ket{junk} \\
		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 - \tB_1}{-2\sin(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
		=(\1 \x \paulix{2} \ket{\EPR{2}}) \x \ket{junk} 
	\end{align*}
	where $\tB_0 = \tB_0^0 - \tB_0^1$ and $\tB_1 = \tB_1^0 - \tB_1^1$.
\end{lemma}
\begin{proof}
Note that $\tA_x^a \tB_y^b$ means $\tA_x^a \x \tB_y^b$ in the following proof.

@@

%-----------------------------------------------------------------
\subsection{Proof}
%-----------------------------------------------------------------
\hl{This subsection needs to be formalized.}
By Lemma~$4.3$ of \cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
of the linear system game: 
For each variable $\{ x_i \}_{i=1}^n$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
The condition that they agree with assignment to variables means that 
\begin{align}
	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
\end{align}
and the condition that Alice's assignments satisfy the constraint means that 
\begin{align}
	\Tr(\rho_A \Pi_{j: A_{ij} \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m
\end{align}
where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$, so for  any $\ket{v} \in \supp(\rho_A)$,
we have 
\begin{align}
\Pi_{j:A_{ij} \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m.
\end{align}
Since the relation $uxu^\dagger = x^2$ is embedded in this linear system game, we know
\begin{align}
	A_3A_4 A_1A_2 (A_3A_4)^\dagger \ket{v}= (A_1A_2)^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
\end{align}
How $u$ and $x$ are splitted into order-$2$ generators can be found in Appendix~\ref{sec:construct}.
For simplicity, we define $X = A_1A_2$ and $U=A_3A_4$ such that
the condition is equivalent to
\begin{align}
	\label{eq:ux_relation}
	UXU^\dagger \ket{v} = X^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
\end{align}
We will come back to the implication of this condition later.
